Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-05-06 paper/paper.tex
defining 'partially observable'

RL is a problem-solving technique in which,
through repeated interactions with an\textit{environment},
an agent learns to reach goals and optimize reward signals
in an iterative trial-and-error fashion (Fig. \ref{fig:rl}).
At a given moment, each taken \textit{action} $a$ triggers a change
in the \textit{state} of the environment
$s \rightarrow s'$, accompanied by environmental feedback signals as \textit{reward}
$r = r(s, a)$ collected by the agent.
If the collected reward outcome yields a negative value it can be
more naturally interpreted as \textit{punishment}.
In this view, the environment is partially controlled by
the action of the agent and the reward can be thought
of as satisfaction \textemdash or aversion \textemdash accompanying the execution of
a particular action.
% Action may be delayed to achieve substantial increases in expected reward
% that is expected to grow with time.

The environment is generally taken as \textit{stochastic},
that is, changing in random ways. In addition,
the environment is only \textit{partially observed}
in the sense that \textbf{XXX [Please Define without using the same words]}
only part of the current state is observed by
the agent \citep{starkweather2017dopamine}.
We assume that volatility of the environment
is realistic in a computational model which sets out
to explain DMN functions of the human brain.
% XXX: the following passage is already in the introduction
% Indeed, it is known that the more the external world is predictable,
% the more mental activity becomes detached from the actual sensory inputs
% \citep{antrobus1966studies, pope1978regulation},
% the more stimulus-independent thoughts occur, and
% the higher the neural activity in the DMN.
% Conversely, the more the currently executed task is unknown and unpracticed,
% the lower the DMN activity
% \citep{filler1973daydreaming, teasdale1995stimulus}.
% %
% These ``offline'' processes may however contribute to
% optimizing control of the organism.
% Such a framework of DMN funtion based on reinforcement learning
% can naturally embed human behavior
% in the tension between exploitative action with immediate gains and
% explorative action with longer-term reward schedules
% \citep{dayan2008decision}.
We argue that a functional account of the DMN based on RL
can naturally embed human behavior
in the tension between exploitative action with immediate gains and
explorative action with longer-term reward outcomes
\citep{dayan2008decision}.

@@

  % \textbf{XXX Elvis to Elvis: clarify the notion of greed. Add a paragraph on the exploitation vs exploration dilemma, and end with a conclusion saying the DMN probably does epsilon-greedy
  %   or softmax.}

>>>>

RL is a problem-solving technique in which,
through repeated interactions with an\textit{environment},
an agent learns to reach goals and optimize reward signals
in an iterative trial-and-error fashion (Fig. \ref{fig:rl}).
At a given moment, each taken \textit{action} $a$ triggers a change
in the \textit{state} of the environment
$s \rightarrow s'$, accompanied by environmental feedback signals as \textit{reward}
$r = r(s, a,s')$ collected by the agent.
If the collected reward outcome yields a negative value it can be
more naturally interpreted as \textit{punishment}.
In this view, the environment is partially controlled by
the action of the agent and the reward can be thought
of as satisfaction \textemdash or aversion \textemdash accompanying the execution of
a particular action.
% Action may be delayed to achieve substantial increases in expected reward
% that is expected to grow with time.

The environment is generally taken as \textit{stochastic},
that is, changing in random ways. In addition, the environment is only
\textit{partially observable} in the sense only limited aspects of the environment's
state are accessible to --or can be sensed by-- the agent's sensors.
\citep{starkweather2017dopamine}.
We assume that volatility of the environment
is realistic in a computational model which sets out
to explain DMN functions of the human brain.
% XXX: the following passage is already in the introduction
% Indeed, it is known that the more the external world is predictable,
% the more mental activity becomes detached from the actual sensory inputs
% \citep{antrobus1966studies, pope1978regulation},
% the more stimulus-independent thoughts occur, and
% the higher the neural activity in the DMN.
% Conversely, the more the currently executed task is unknown and unpracticed,
% the lower the DMN activity
% \citep{filler1973daydreaming, teasdale1995stimulus}.
% %
% These ``offline'' processes may however contribute to
% optimizing control of the organism.
% Such a framework of DMN funtion based on reinforcement learning
% can naturally embed human behavior
% in the tension between exploitative action with immediate gains and
% explorative action with longer-term reward schedules
% \citep{dayan2008decision}.
We argue that a functional account of the DMN based on RL
can naturally embed human behavior
in the tension between exploitative action with immediate gains and
explorative action with longer-term reward outcomes
\citep{dayan2008decision}.

@@
